Quantum-assisted unsupervised data clustering

### 2020-05-08 manuscript.tex
resolving issue #47

%%%%%
\begin{figure}[t]
	\includegraphics[width=\columnwidth]{qcircuit.eps}
	\caption{
		Quantum circuit for the quantum parallelized Hamming distance calculating  between all pairs of binary vectors from two sets ${X}$ and ${Y}$ encoded \cite{trugenberger2001} in $X$ and $Y$ quantum registers   respectively.
		First, we encoded information about pairwise different qubits in a quantum state of the $X$-register with applying the CNOT gates. 
		Second, Hamming distance values are extracted into the amplitudes of superposition with the controled rotation around $z$-axis gate~(\ref{eq:controled_rotation}) and Hadamard gates. 
		Finally, a quantum state of the $X$-register returned to the initial basis for information retrieval. 	
	} 
	\label{fig:qcircuit}
\end{figure}
%%%%%

>>>>

%%%%%
\begin{figure}[t]
	\includegraphics[width=\columnwidth]{qcircuit.eps}
	\caption{
		Quantum circuit for the quantum parallelized Hamming distance calculating  between all pairs of binary vectors from two sets ${X}$ and ${Y}$ encoded in $X$ and $Y$ quantum registers   respectively.
		First, we encoded information about pairwise different qubits in a quantum state of the $X$-register with applying the CNOT gates. 
		Second, Hamming distance values are extracted into the amplitudes of superposition with the controled rotation around $z$-axis gate~(\ref{eq:controled_rotation}) and Hadamard gates. 
		Finally, a quantum state of the $X$-register returned to the initial basis for information retrieval. 	
	} 
	\label{fig:qcircuit}
\end{figure}
%%%%%
